Global Climate of the Ultra-Hot Jupiter WASP-103b from \HST\ and Spitzer Phase Curve Observations

### 2017-10-08 ms.tex
model

\title{Phase Curves of WASP-103b}

@@

@@

\begin{deluxetable}{ccccc}
	%\tabletypesize{\small}
	\tablenum{1}
	\tablewidth{0pt}
	\tablecaption{Summary of Photometric Observations of WASP-103}
	\tablehead{
		\colhead{Observing} & \colhead{} & \colhead{Date Range} &
		\colhead{Sigma} & \colhead{Seasonal Mean}  \\

		\colhead{Season} & \colhead{$N_{obs}$} & \colhead{(HJD $-$ 2,400,000)} &
		\colhead{(mag)} & \colhead{(mag)}}%   \\

@@

\section{Light Curve Fits}
which orbits/data
ellipsoidal variations/doppler beaming

The raw data exhibit time-dependent systematic trends typically seen in WFC3 light curves, which we correct using a systematics model of the form:

@@

and fit the systematics with the BLISS mapping technique \citep{stevenson12}. This technique creates a map of the intrapixel sensitivity while simultaneously fitting for other systematics and the physical parameters of the system. In addition to the intrapixel sensitivity map, we fit the data for a linear trend in time and used the same transit, eclipse, and phase variation model as in Equation%\;\ref{eq:model}.

>>>>

\title{Global Climate of the Ultra-Hot Jupiter WASP-103b from \HST\ and Spitzer Phase Curve Observations}

@@

Talk about other WFC3 papers (Star Cartier, etc)

@@

\begin{deluxetable}{ccccc}
	%\tabletypesize{\small}
	\tablenum{1}
	\tablewidth{0pt}
	\tablecaption{Photometric Observations of WASP-103}
	\tablehead{
		\colhead{Observing} & \colhead{} & \colhead{Date Range} &
	\colhead{Sigma} & \colhead{Seasonal Mean} }% \\

%		\colhead{Season} & \colhead{$N_{obs}$} & \colhead{(HJD $-$ 2,400,000)} &
%		\colhead{(mag)} & \colhead{(mag)}}%   \\

@@

\section{Light Curve Fits}
We fit the \HST\ and \Spitzer\ phase curves independently. For each light curve fit, we used a two-component model:
 one component models the physical signal (the planet's thermal phase variation) and the other models the instrument systematics.

\subsection{Physical Model}
We explored several different models for the planet's thermal phase variation.

two-temperature model, with a uniform dayside temperature $T_d$ and a uniform nightside temperature $T_n$. also temperature map generated with spherical harmonics, the most general.  Physically-motivated kinematic model from \cite{zhang16}, which has just three free parameters (the nightside temperature $T_n$, the change in temperature from day-to-night side $\Delta_T$, and the ratio of radiative to advective timescales $\xi$). The kinematic model makes several simplifying assumptions (e.g, that the wind speed and direction are constant), but it reproduces GCM simulations fairly well.

We also fit a sine curve.

\subsubsection{Ellipsoidal Variations and Doppler Beaming}
ellipsoidal variations/doppler beaming

\subsection{Systematics Models}
Both the \HST\ and \Spitzer\ phase curves have systematic noise caused by variations in the sensitivity of the instrument over time. For the WFC3 data, the dominant systematic is an orbit-long exponential trend due to charge traps filling up over successive exposures \citep{zhu17}. For \Spitzer\, the intrapixel sensitivity effect is the primary source of noise. The detector's pixels do not have uniform sensitivity, so slight changes in telescope pointing cause the recorded flux to vary.

\subsubsection{\HST\ Systematics}
The raw data exhibit time-dependent systematic trends typically seen in WFC3 light curves, which we correct using a systematics model of the form:

@@

\subsubsection{\Spitzer\ Systematics}
and fit the systematics with the BLISS mapping technique \citep{stevenson12}. This technique creates a map of the intrapixel sensitivity while simultaneously fitting for other systematics and the physical parameters of the system. In addition to the intrapixel sensitivity map, we fit the data for a linear trend in time and used the same transit, eclipse, and phase variation model as in Equation%\;\ref{eq:model}.

which orbits/data
